Supplementary Information

### 2021-02-01 doc/manuscript/MEE_manuscript_SI.Rmd
knit in new figures
https://github.com/EcoClimLab/ForestGEO-climate-sensitivity/issues/109

![`r recruitment_plot_SCBI_legend` `r recruitment_generic_legend`](tables_figures/SI_figures/recruitment_years/Recrutement_years_SCBI.png){ width=47% }
\newpage

>>>>

![`r recruitment_plot_SCBI_legend` `r recruitment_generic_legend`](tables_figures/SI_figures/recruitment_years/Recrutement_years_SCBI.png){ width=90% }
